Verifying Demonstrations

### 2020-03-13 paper/conclusions.tex
Improves conclusion scenario (fixes #46)

In this paper, we have adapted the Schnorr protocol as a
distance-bounding protocol.  It allows to construct distance-bounding
general attribute-based authentication, more general attributes than
provided by previous \ac{DB} ones.  With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than
18 but younger than 40 without revealing her actual age, and at the
same time Bob can be sure that Alice is not just relaying messages
from her older sister Carol.

>>>>

In this paper, we have adapted the Schnorr protocol as a
distance-bounding protocol.  It allows to construct distance-bounding
general attribute-based authentication, more general attributes than
provided by previous \ac{DB} ones.  With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than 18 
(without revealing her actual age), has a cinema subscription which is not 
\enquote{double spent} by someone else at the same time and, at the same time, 
Bob can be sure that Alice is not just relaying messages from her older sister 
Carol or \ac{DBMF} relaying the subscription from some unsuspecting stranger.
